\ttitle

### 2013-11-06 Chapters/Chapter1.tex
WIP

>>>>

\begin{figure}
  \centering
    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{./Figures/chapter1/thesis_goal.pdf}
  \caption[Thesis goal]{The goal of this thesis. The scope of this thesis is Temporal Segmentation, which can be useful in the context of Temporal Classification. Given a data set, we apply the construction of \gls{oc-svm} models as a form of dimensionality reduction. Using the reduced representation, being the radius $R$ of the constructed hypersphere, we apply direct change detection methods. The detected change points can support the classification of homogeneous segments of data.}
  \label{fig:thesis_goal}
\end{figure}

### 2013-11-06 Chapters/Chapter3/one_class_svm.tex
WIP

\subsection{\acrlong{nu-svm}}\label{subsec:nu-svm}
The first of the \gls{oc-svm} methods we will discuss is often referred to as \gls{nu-svm} and introduced by Sch\"olkopf \etal \cite{scholkopf1999support}.
Instead of estimating the density function of an distribution $P$, it focuses on an easier problem: the algorithm find regions in the input where the ``probability density lives''.
This results in a function such that most of the data is in the region where the function is nonzero.

@@

\TODO{Note that \gls{svdd} and \gls{nu-svm} have identical solutions when data is preprocessed to have unit form (in the case of \gls{nu-svm}) \cite{tax2002uniform}.}

@@

Kernels for Support Vector Classifiers were first (?) used by Vapnik \cite{vapnik1998statistical}.

>>>>

\subsection{\acrlong{nu-svm}}\label{subsec:nu-svm}
\TODO{Check notations with book of Scholkopf \cite{scholkopf2002learning}, chapter 8, page 227.} \\
The first of the \gls{oc-svm} methods we will discuss is often referred to as \gls{nu-svm} and introduced by Sch\"olkopf \etal \cite{scholkopf1999support}.
Instead of estimating the density function of an distribution $P$, it focuses on an easier problem: the algorithm find regions in the input where the ``probability density lives''.
This results in a function such that most of the data is in the region where the function is nonzero.

@@

\TODO{Note that \gls{svdd} and \gls{nu-svm} have identical solutions when data is preprocessed to have unit form (in the case of \gls{nu-svm}) \cite{tax2002uniform}. and the \gls{rbf} kernel is used. Page 234 of \cite{scholkopf2002learning}.}

@@

Kernels for Support Vector Classifiers were first (?) used by Vapnik \cite{vapnik1998statistical}. \\

Use Chapter 2 from ``Learning with kernels'', \cite{scholkopf2002learning}.

### 2013-11-06 Chapters/Chapter4/model_construction.tex
WIP

From experiments it shows that the (online) \gls{isvdd} method results in less false alarms than the static \gls{svdd}.
An explanation for this is that \gls{isvdd} follows the changing data distribution, \ie small changes over time.
Such changes are a drift in mean or increase in frequency.
The \gls{isvdd} algorithm continuously re-models the \gls{svm} representation.
For our method we use the re-modeling capability of the \gls{isvdd} algorithm to obtain change indication measure.
The following section will discuss the properties used from the constructed \gls{oc-svm} model at every loop-step of the algorithm.

\TODO{make more explicit that the re-modeling is a strong property for our change-detection method.}

>>>>

From experiments it shows that the (online) \gls{isvdd} method results in less false alarms than the static \gls{svdd}.
An explanation for this is that \gls{isvdd} follows the changing data distribution, \ie small changes over time.
Such changes are a drift in mean or increase in frequency.
The \gls{isvdd} algorithm continuously re-models the \gls{svm} representation.
This re-modeling of the \gls{svm} representation is beneficial for our purpose, since we are only interested in sudden changes between activities.
The following section will discuss the features extracted from the constructed \gls{oc-svm} model at every loop-step of the algorithm, before Section~\ref{sec:method_change_detection} describes how these features are used to detect change.
